\documentclass[12pt,a4paper]{report}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{titlesec}
\usepackage{fancyhdr} 
\usepackage{lipsum} 
\usepackage{amsmath} % For mathematical formatting
\usepackage{graphicx}
\usepackage{color}
\usepackage{listings}
\usepackage{newtxtext} % Times New Roman for text
\usepackage{newtxmath} % Times New Roman for math
\titleformat{\chapter}[hang]{\bfseries\Large}{\thechapter.}{1em}{}
\titleformat{\section}[hang]{\bfseries\large}{\thesection}{1em}{}
%\usepackage{hyperref}
\usepackage{xcolor, colortbl}
\setlength{\topmargin}{-0.5in}
\setlength{\oddsidemargin}{0.5in}
\setlength{\evensidemargin}{0.5in}
\setlength{\textwidth}{6in}
\setlength{\textheight}{9in}
\setstretch{1.5}
\usepackage{pgfplots}
\usepackage{acronym}
\usepackage{pgfplots}
\pgfplotsset{compat=1.17}

\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\definecolor{lightblue}{rgb}{0.678, 0.847, 0.902}
\definecolor{lightpink}{rgb}{1.0, 0.71, 0.76}
\definecolor{lightcoral}{rgb}{0.941, 0.502, 0.502}
\definecolor{peachpuff}{rgb}{1.0, 0.99, 0.99}

\lstdefinestyle{mystyle}{
	backgroundcolor=\color{peachpuff},
	commentstyle=\color{codegray},
	keywordstyle=\color{blue},
	numberstyle=\tiny\color{blue},
	stringstyle=\color{codepurple},
	basicstyle=\ttfamily\footnotesize,
	breakatwhitespace=false,
	breaklines=true,
	captionpos=b,
	keepspaces=true,
	numbers=left,
	numbersep=5pt,
	showspaces=false,
	showstringspaces=false,
	showtabs=false,
	tabsize=2
}
\lstset{style=mystyle}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\thepage}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt} 

\begin{document}
	
	\pagenumbering{arabic}
	\setcounter{page}{27}
	
	\section*{References}	
\begin{enumerate}
	\item A. M. Abdelsalam and M. S. Sayed, ``Real-time defects detection system for orange citrus fruits using multi-spectral imaging,'' in \textit{Proc. IEEE 59th Int. Midwest Symp. Circuits Syst. (MWSCAS)}, Oct. 2016, pp. 1--4.
	\item N. K. Bahia, R. Rani, A. Kamboj, and D. Kakkar, ``Hybrid feature extraction and machine learning approach for fruits and vegetable classification,'' \textit{Pertanika J. Sci. Technol.}, vol. 27, no. 4, pp. 1693--1708, 2019.
	\item T. Tao and X. Wei, ``A hybrid CNN–SVM classifier for weed recognition in winter rape field,'' \textit{Plant Methods}, vol. 18, no. 1, p. 29, Dec. 2022.
	\item Z. Zha, D. Shi, X. Chen, H. Shi, and J. Wu, ``Classification of appearance quality of red grape based on transfer learning of convolution neural network,'' \textit{Tech. Rep.}, 2023.
	\item S. R. N. Appe, G. Arulselvi, and G. Balaji, ``Tomato ripeness detection and classification using VGG based CNN models,'' \textit{Int. J. Intell. Syst. Appl. Eng.}, vol. 11, no. 1, pp. 296--302, 2023.
	\item R. G. de Luna, E. P. Dadios, A. A. Bandala, and R. R. P. Vicerra, ``Size classification of tomato fruit using thresholding, machine learning, and deep learning techniques,'' \textit{AGRIVITA J. Agricult. Sci.}, vol. 41, no. 3, pp. 586--596, Oct. 2019.
	\item H. S. Mputu, A. Abdel-Mawgood, A. Shimada, and M. S. Sayed, ``Tomato quality classification based on transfer learning feature extraction and machine learning algorithm classifiers,'' \textit{IEEE Access}, vol. 12, pp. 8283--8295, 2024, doi: 10.1109/ACCESS.2024.3352745.
	\item W. Xu, Y.-L. Fu, and D. Zhu, ``ResNet and its application to medical image processing: Research progress and challenges,'' \textit{Comput. Methods Programs Biomed.}, vol. 240, p. 107660, 2023, doi: 10.1016/j.cmpb.2023.107660.
	\item C. Szegedy, V. Vanhoucke, S. Ioffe, J. Shlens, and Z. Wojna, ``Rethinking the Inception Architecture for Computer Vision,'' in \textit{Proc. IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2016, pp. 2818--2826, doi: 10.1109/CVPR.2016.308.
	\item K. Dong, C. Zhou, Y. Ruan, and Y. Li, ``MobileNetV2 Model for Image Classification,'' in \textit{Proc. Int. Conf. Inf. Technol. Comput. Appl. (ITCA)}, 2020, pp. 476--480, doi: 10.1109/ITCA52113.2020.00106.
	\item S. G. Siddarth and S. Chokkalingam, ``DenseNet 121 Framework for Automatic Feature Extraction of Diabetic Retinopathy Images,'' in \textit{Proc. Int. Conf. Emerg. Syst. Intell. Comput. (ESIC)}, 2024, pp. 338--342.
	 \item V.-T. Hoang and K.-H. Jo, ``Practical Analysis on Architecture of EfficientNet,'' in \textit{Proc. Int. Conf. Hum. Syst. Interact. (HSI)}, 2021, pp. 1--4.
	\item W. Lai, T. Zhang, T. L. Lam, and Y. Gao, ``Vision-Language Model-based Physical Reasoning for Robot Liquid Perception,'' in \textit{Proc. 2024 IEEE/RSJ Int. Conf. Intelligent Robots and Systems (IROS)}, 2024, pp. 9652--9659.
	\item X. Li, C. Wen, Y. Hu, Z. Yuan, and X. X. Zhu, ``Vision-Language Models in Remote Sensing: Current progress and future trends,'' \textit{IEEE Geoscience and Remote Sensing Magazine}, vol. 12, no. 2, pp. 32--66, 2024, doi: 10.1109/MGRS.2024.3383473.
	\item J. Redmon, S. Divvala, R. Girshick, and A. Farhadi, ``You Only Look Once: Unified, Real-Time Object Detection,'' in \textit{Proc. 2016 IEEE Conf. Comput. Vis. Pattern Recognit. (CVPR)}, 2016, pp. 779--788, doi: 10.1109/CVPR.2016.91.
	\item A. K. Sangaiah, F.-N. Yu, Y.-B. Lin, W.-C. Shen, and A. Sharma, ``UAV T-YOLO-Rice: An Enhanced Tiny Yolo Networks for Rice Leaves Diseases Detection in Paddy Agronomy,'' \textit{IEEE Trans. Network Sci. Eng.}, vol. 11, no. 6, pp. 5201--5216, 2024, doi: 10.1109/TNSE.2024.3350640.
	\item J. Wang, T. Wang, W. Cai, L. Xu, and C. Sun, ``Boosting Efficient Reinforcement Learning for Vision-and-Language Navigation With Open-Sourced LLM,'' \textit{IEEE Robotics and Automation Letters}, vol. 10, no. 1, pp. 612--619, 2025, doi: 10.1109/LRA.2024.3511402.
	\item S. S. Teja Gontumukkala, Y. S. Varun Godavarthi, B. R. Ravi Teja Gonugunta, R. Subramani, and K. Murali, ``Analysis of Image Classification using SVM,'' in \textit{Proc. 2021 12th Int. Conf. Comput. Commun. Networking Technol. (ICCCNT)}, 2021, pp. 1--6, doi: 10.1109/ICCCNT51525.2021.9579803.
	\item X. Sun, L. Liu, H. Wang, W. Song, and J. Lu, ``Image classification via support vector machine,'' in \textit{Proc. 2015 4th Int. Conf. Comput. Sci. Network Technol. (ICCSNT)}, 2015, vol. 1, pp. 485--489, doi: 10.1109/ICCSNT.2015.7490795.
	\item D. Patidar, B. C. Shah, and M. R. Mishra, ``Performance analysis of K Nearest Neighbors image classifier with different wavelet features,'' in \textit{Proc. 2014 Int. Conf. Green Comput. Commun. Electr. Eng. (ICGCCEE)}, 2014, pp. 1--6, doi: 10.1109/ICGCCEE.2014.6922459.
	\item E. C. Ozan, E. Riabchenko, S. Kiranyaz, and M. Gabbouj, ``A vector quantization based k-NN approach for large-scale image classification,'' in \textit{Proc. 2016 Int. Conf. Image Process. Theory, Tools Appl. (IPTA)}, 2016, pp. 1--6, doi: 10.1109/IPTA.2016.7821010.
	\item C. Agarwal and A. Sharma, ``Image understanding using decision tree based machine learning,'' in \textit{Proc. 5th Int. Conf. Inf. Technol. Multimedia (ICIMU)}, 2011, pp. 1--8, doi: 10.1109/ICIMU.2011.6122757.
	\item H. Liu, M. Cocea, and W. Ding, ``Decision tree learning based feature evaluation and selection for image classification,'' in \textit{Proc. 2017 Int. Conf. Mach. Learn. Cybernet. (ICMLC)}, 2017, vol. 2, pp. 569--574, doi: 10.1109/ICMLC.2017.8108975.
\end{enumerate}
	
\end{document}

